Review of Assigned Readings

### 2017-12-29 paper/paper.tex
added bitcoin part

		\section{Brief Background and Data Collection}
		\itshape\textbf {Bitcoin}\\
		\textnormal {(Text for Bitcoin) Input Alen: Explain why bitcoin is of relevance, short intro what bitcoin is}\\

>>>>

		\section{Brief Background and Data Collection}
		\itshape\textbf {Bitcoin}\\
		\textnormal {After the global financial crisis, Satoshi Nakamoto (2008, p. 1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions. Starting from his whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions (blockchain) has been developed (Nakamoto, 2008, p. 1).\newline
Today, Bitcoin is the most popular of over 1300 so-called cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/). Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes. Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017, Forbes 2017, Yermack, 2013). Kristoufek (2015, Discussion) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term. However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency. Kristoufek (2015) further explains the correlation is most evident in the long run.  During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Discussion). These findings are in line with other researchers’ findings (see Garcia et. al 2014, Kondor et al. 2014).\newline
One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices. (Mao et al.,2015, p. 3) A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data. Based on analysis of the influence of twitter bullishness on the stock market by Mao et al. (2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.
 }\\
